Multivariate Neuroanalysis with ANTsR: Application to Supervised Brain Segmentation with Concatenated Random Forests

### 2013-06-15 ANTsRS/paper.tex
McLovin

\author[label1]{Nicholas J.~Tustison
  \fnref{label0}}
  \fntext[label0]{\scriptsize Corresponding author:  PO Box 801339, Charlottesville, VA 22908; T:  434-924-7730; email address:  ntustison@virginia.edu.
  }
\author[label2]{K.~L.~Shrinidhi}
\author[label2]{Jeffrey T.~Duda}
\author[label2]{Philip A.~Cook}
\author[label1]{Christopher Durst}
\author[label1]{James C.~Gee}
\author[label1]{Murray C.~Grossman}
\author[label1]{Max Wintermark}
\author[label2]{Brian B.~Avants}
\address[label1]{Department of Radiology and Medical Imaging, University of Virginia, Charlottesville, VA}
\address[label2]{Penn Image Computing and Science Laboratory, University of Pennsylvania,
                Philadelphia, PA}

@@

Given a set of training data consisting of 
labeled (csf, gray matter, white matter, edema, and tumor),
multimodal brain image data, 
supervised brain segmentation entails the generation of a 
statistical model from such training data which can
then be extended to testing data, i.e. unlabeled 
brain data.  In subsequent sections, we introduce the generic
{\it random forest} modeling framework which takes as input
a set of {\it feature images} (also described in a later section)
and labels for each training subject 
and outputs a statistical model.  This model, in turn, can then
be used to provide a probabilistic estimate of the labels in an
unlabeled subject.

>>>>

\author[label1]{Nicholas J.~Tustison
  \fnref{label0}}
  \fntext[label0]{\scriptsize Corresponding author:  PO Box 801339, Charlottesville, VA 22908; T:  434-924-7730; email address:  ntustison@virginia.edu.
  }
\author[label2]{K.~L.~Shrinidhi}
\author[label2]{Jeffrey T.~Duda}
\author[label2]{Philip A.~Cook}
\author[label1]{Christopher Durst}
\author[label1]{Max Wintermark}
\author[label1]{James C.~Gee}
\author[label1]{Murray C.~Grossman}
\author[label2]{Brian B.~Avants}
\address[label1]{Department of Radiology and Medical Imaging, University of Virginia, Charlottesville, VA}
\address[label2]{Penn Image Computing and Science Laboratory, University of Pennsylvania,
                Philadelphia, PA}

@@

Given a set of training data consisting of 
labeled (csf, gray matter, white matter, edema, and tumor),
multimodal brain image data, 
supervised brain segmentation entails the generation of a 
statistical model from such training data which can
then be extended to testing data, i.e. unlabeled 
brain data.  In subsequent sections, we detail the generic
{\it random forest} modeling framework which takes as input
a set of {\it feature images} (also described in a later section)
and labels for each training subject 
and outputs a statistical model.  This model, in turn, can then
be used to provide a probabilistic estimate of the labels in an
unlabeled subject.
